sensiAnPaper1All

### 2016-01-26 sensiAnPaper1All.Rmd
add options for extended experiments

  nScenarios <- 10  
  #nScenarios <- 100
  #nScenarios <- 1000
  ## do model runs
  listOutMix <- sensiAnPaperPart( nScenarios, insecticideUsed = 'mixture' )
  listOutI1 <- sensiAnPaperPart( nScenarios, insecticideUsed = 'insecticide1' )
  listOutI2 <- sensiAnPaperPart( nScenarios, insecticideUsed = 'insecticide2' )

@@

@@

```{r}
  ## to load previously saved runs
  load(file=paste0(outFolder,'listOutMix_1000.rda'))
  load(file=paste0(outFolder,'listOutI1_1000.rda'))
  load(file=paste0(outFolder,'listOutI2_1000.rda'))

>>>>

  #nScenarios <- 10  
  #nScenarios <- 100
  nScenarios <- 1000

  #to run 'extended' or not
  experiment <- 'extended' #'curtis'

  ## do model runs
  listOutMix <- sensiAnPaperPart( nScenarios, insecticideUsed = 'mixture', experiment=experiment )
  listOutI1 <- sensiAnPaperPart( nScenarios, insecticideUsed = 'insecticide1', experiment=experiment )
  listOutI2 <- sensiAnPaperPart( nScenarios, insecticideUsed = 'insecticide2', experiment=experiment )

@@

  save(listOutMix, file=paste0(outFolder,'listOutMix_ex1000.rda'))
  save(listOutI1, file=paste0(outFolder,'listOutI1_ex1000.rda'))
  save(listOutI2, file=paste0(outFolder,'listOutI2_ex1000.rda'))

@@

```{r}
  ## to load previously saved runs
#   load(file=paste0(outFolder,'listOutMix_1000.rda'))
#   load(file=paste0(outFolder,'listOutI1_1000.rda'))
#   load(file=paste0(outFolder,'listOutI2_1000.rda'))

  load(file=paste0(outFolder,'listOutMix_ex1000.rda'))
  load(file=paste0(outFolder,'listOutI1_ex1000.rda'))
  load(file=paste0(outFolder,'listOutI2_ex1000.rda'))
